---
header-includes:
- \usepackage{authblk}
- \usepackage{amsmath}
- \usepackage{longtable}
- \usepackage{multirow}
- \usepackage{rotating}
- \usepackage{float}
- \usepackage{array}
- \usepackage{calc}
- \usepackage{mwe}
- \usepackage[titletoc,toc,page]{appendix}
- \usepackage{amsthm}
- \usepackage{subcaption}
- \usepackage{graphicx}
- \usepackage[T1]{fontenc}
- \usepackage[utf8]{inputenc}
- \usepackage{lmodern}
- \usepackage{url}
- \usepackage[svgnames]{xcolor}
- \usepackage{pdfcolmk}
- \usepackage{tikz}
- \usepackage{pifont}
- \usepackage{adjustbox,lipsum}
- \usepackage{fancyhdr, graphicx}
- \usepackage{placeins}
- \usepackage{lastpage}
- \usepackage{fancyhdr}
- \pagestyle{fancy} 

output:
  pdf_document: null
  word_document:
    fig_caption: yes
    fig_height: 3.5
    fig_width: 4
    toc: yes
    toc_depth: 2
---
```{r setup, include=FALSE}
#install.packages("tigerstats")
#install.packages("abd")
#install.packages("mosaic")
#library(mosaicCore)
library(ggplot2)
library(knitr)
knitr::opts_chunk$set(fig.path = 'figures/',
                      echo = FALSE, warning = FALSE, message = FALSE)

#- \newcommand{\chapfnt}{\fontsize{20}{19}}
#- \newcommand{\secfnt}{\fontsize{20}{17}}
```

---
- \theoremstyle{remark}
- \newtheorem{remark}{Remark}[section]

---
\newpage
\cfoot{\thepage\ of \pageref{LastPage}}



\begin{figure}
\centering
\begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=0.50\linewidth]{Blank}
\end{subfigure}
\end{figure}


\begin{figure}
\centering
\begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{HDRUK}
\end{subfigure}
\end{figure}



\begin{figure}
\centering
\begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=0.70\linewidth]{Uni}
\end{subfigure}
\end{figure}

\vskip4cm
\begin{center}
\bfseries\Large {Epilepsy, anti-epileptic drugs and the risk of cardiovascular events}\\


\vskip4cm
\small This document provides an update of work \\
\small that has been completed todate based on the agreed plan for project SAIL0758.\\
\small The IGRP application  SAIL0758 for this project has been approved. \\

\vskip4cm
\ Health Data Research UK, Swansea University\\


\ Date:February 2019
\end{center}

\newpage
#  **Introduction**



```{r packages&libraries,message=FALSE, comment=NA,echo=FALSE}

## if source file hasn't been recognized check the folder directory
#pop up a login box (may be behind current window)

##Packages: 
#if you get an error with the name of any packages: download the packages outside the markdown document.
#install.packages ("RODBC");
#install.packages("Cairo");
#install.packages ("lattice");
#install.packages ("sqldf");
#install.packages ("getopt");

library(RODBC);
library (Cairo);
library (lattice);
library (getopt);
library(dplyr)
library(psych)
library(rmarkdown)


#Include the file login_box.r in your project. You may have to include the full
#path to the file depending on how R is configured.
#obtain the longin_box file either via wiki or ask any member of the team

source("S:/0000 - Analysts Shared Resources/r-share/login_box.r");

#Get the login info, using 'yourUsername' as username.

login = getLogin();

#Connect and get the database
sql = odbcConnect('PR_SAIL',login[1],login[2]);
login = 0 # this will make your password anonymous


```

```{r cohort , message=FALSE, comment=NA,echo=FALSE}
#study cohort: using SWORD cohort table

study_start=as.Date("2017-01-01")
study_end= as.Date("2018-01-01")

HAS_cohort = sqlQuery(sql,"
SELECT 	
	A.*, 
	A.CHADSVASC_BL CHADSVASC_BL2,
	A.HASBLED_INR5_BL HASBLED_INR5_BL2,
	A.HASBLED_INR8_BL HASBLED_INR8_BL2, 
	CASE 
	WHEN BASE_AGE < 65 THEN '18-65'
	WHEN BASE_AGE BETWEEN 65 AND 75 THEN '65-74'
	WHEN BASE_AGE >= 75 THEN '75+'
	END AS AGE_CAT
FROM 	SAILW0866V.MSC_HASB_20190807 A
WHERE A.alf_pe IN 
	(
	SELECT * FROM SAILW0866V.ALF_ANALYSED_MSC_20190809
	)
")

#COHORT WITH GP_END_DATE

#TO ADDRESS THE MISSINGNESS OF RECORDS WE PUT THE 6-MONTHS OF GP DATA IN PLACE

#number of cases in the study cohort
HAS_CASE= nrow(HAS_cohort)

HAS_cohort$GNDR_CD = replace(HAS_cohort$GNDR_CD,HAS_cohort$GNDR_CD == "1","Male");
HAS_cohort$GNDR_CD = replace(HAS_cohort$GNDR_CD,HAS_cohort$GNDR_CD == "2","Female");


#avg_followup_yrs =  mean(ep.cohort$STUDY_GP_COVERAGE_DAYS/365.25);

#total_followup_yrs = as.integer(sum(ep.cohort$STUDY_GP_COVERAGE_DAYS/365.25));

#cohort_before_exclusions = nrow(ep_cohort);

```
